\thetitle

### 2008-05-30 paper.tex
Moved trace vs. uniform figure up & out (of paper.tex).

\newcommand{\FHC}{Hern\'andez-Campos~\textit{et~al.}}
\newcommand{\class}[1]{\textsc{\smaller{#1}}}
\newcommand{\model}[1]{\textsf{\smaller{#1}}}
\newcommand{\RFC}[1]{\caps{RFC}~{#1}}

@@

\newcommand{\X}{\mathsf{X}}
\newcommand{\M}{\mathsf{M}}
\newcommand{\E}[1]{\left<#1\right>}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\Qt}{Q_{\text{time}}}
\newcommand{\Qb}{Q_{\text{byte}}}
\newcommand{\Qi}{Q_{\text{ival}}}
\newcommand{\Di}{Q^{-1}_{\text{ival}}}
\newcommand{\ones}[1]{\mathbf{1}_{#1}}
\newcommand{\zeros}[1]{\mathbf{0}_{#1}}
\newcommand{\mat}[1]{\mathbf{#1}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\mean}[1]{\bar{#1}}
\newcommand{\trans}[1]{{#1}^T}
\newcommand{\inner}[2]{{#1}\cdot{#2}}

@@

@@

The rest of the paper is organized as follows. In \Section{motivation} we discuss motivation and related work. The General Matrix Model is presented in \Section{general-matrix-model}. In Sections~\ref{sec:common-properties}~and~\ref{sec:modeling-concepts} we explore how common network properties and modeling concepts can be expressed in the the \caps{GMM} framework. Our experimental and analytical methodology for evaluating traffic models is presented in \Section{methodology}, while the results of our experiments are explained and analyzed in \Section{results}. The ramifications of these results are discussed in \Section{discussion}. Finally, in \Section{conclusions}, we conclude with a discussion of how this research may be applied to current wireless studies, and how it points the way to better traffic models for the future.

@@

The interaction of wireless users and application behavior with the lower layers of the networking stack is characterized by where, when, how much, and to whom data is transmitted. The joint pattern of traffic generation and mobility through time and space completely determines the effect of wireless usage on the lower levels of the network. This is due to the data-agnostic nature of the protocol stack: by design, \caps{IP} networks treat all data in the same manner~\cite{Clark88}.\QoSnote The credibility of conclusions derived from simulation or experimental deployment depends crucially on our confidence that the models used to generate traffic in experiments are sufficiently realistic.

@@

\begin{figure*}[tb]
\begin{center}
\subfloat[node trace]
{\includegraphics[width=1.335in]{flow_topology_trace}\label{fig:flow-topology-trace}}
\subfloat[node uniform]
{\includegraphics[width=1.335in]{flow_topology_uniform}\label{fig:flow-topology-uniform}}
\subfloat[flow trace]
{\includegraphics[width=1.335in]{flow_behavior_trace}\label{fig:flow-behavior-trace}}
\subfloat[flow uniform]
{\includegraphics[width=1.335in]{flow_behavior_uniform}\label{fig:flow-behavior-uniform}}
\subfloat[packet]
{\includegraphics[width=1.335in]{flow_packet_behavior}\label{fig:packet-behavior}}
\caption{Examples illustrating trace (real) versus uniform (na\"ive synthetic) behaviors at the node, flow and packet levels. Figures \ref{fig:flow-topology-trace} and \ref{fig:flow-topology-uniform} show example node behaviors. The width of each line is proportional to the logarithm of the number of flows between the nodes it connects (zero is the Internet gateway). Uniform and trace flow behavior examples are plotted in Figures \ref{fig:flow-behavior-trace} and \ref{fig:flow-behavior-uniform}. The time axis indicates when flows start and end; the width of each flow line is proportional to the logarithm of its data rate. Figure \ref{fig:packet-behavior} compares uniform (i.e. \caps{CBR}) packet behavior with the trace of an actual flow. In the uniform model, the cumulative data sent increases smoothly over time, whereas in the actual packet trace, the transmissions are variable both in size and in inter-packet interval, leading to a ``lumpy'' cumulative data plot.}
\label{fig:trace-vs-uniform}
\end{center}
\vspace{-1.25em}
\end{figure*}

>>>>

\newcommand{\FHC}{Hern\'andez-Campos~\textit{et~al.}}
\newcommand{\class}[1]{\textsc{#1}}
\newcommand{\model}[1]{\textsf{#1}}
\newcommand{\RFC}[1]{\caps{RFC}~{#1}}

@@

\newcommand{\X}{\mathsf{X}}
\newcommand{\M}{\mathsf{M}}
\newcommand{\E}[1]{\left<#1\right>}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\Qt}{Q_{\text{time}}}
\newcommand{\Qb}{Q_{\text{byte}}}
\newcommand{\Qi}{Q_{\text{ival}}}
\newcommand{\Di}{Q^{-1}_{\text{ival}}}
\newcommand{\ones}[1]{\mathbf{1}_{#1}}
\newcommand{\zeros}[1]{\mathbf{0}_{#1}}
\newcommand{\mat}[1]{\mathbf{#1}}
\newcommand{\mean}[1]{\bar{#1}}
\newcommand{\trans}[1]{{#1}^T}
\newcommand{\inner}[2]{{#1}\cdot{#2}}

@@

\input{trace_vs_uniform}

@@

The rest of the paper is organized as follows. In \Section{motivation} we discuss motivation and related work. The General Matrix Model is presented in \Section{general-matrix-model}. In Sections~\ref{sec:common-properties}~and~\ref{sec:modeling-concepts} we explore how common network properties and modeling concepts can be expressed in the the \caps{GMM} framework. Our experimental and analytical methodology for evaluating traffic models is presented in \Section{methodology}, while the results of our experiments are explained and analyzed in \Section{results}. The ramifications of these results are discussed in \Section{discussion}. Finally, in \Section{conclusions}, we conclude with a discussion of how this research may be applied to current wireless studies. %, and how it points the way to better traffic models for the future.

@@

The interaction of network users and application behavior with the lower layers of the networking stack is characterized by where, when, how much, and to whom data is transmitted. The joint pattern of traffic generation and mobility through time and space completely determines the effect of wireless usage on the lower levels of the network. This is due to the data-agnostic nature of the protocol stack: by design, \caps{IP} networks treat all data in the same manner~\cite{Clark88}.\QoSnote The credibility of conclusions derived from simulation or experimental deployment depends crucially on our confidence that the models used to generate traffic in experiments are sufficiently realistic. \Figure{trace-vs-uniform} demonstrates how drastically different network traffic appears when assumptions of uniform behavior at various levels are imposed. Assumptions of independence are not as visually dramatic, but we will demonstrate that they distort the performance characteristics of networks almost as much---or more---than uniform models.

@@
